# Data Quality Analysis

## Required software and packages

1.  R Software

2.  RStudio

3.  Following packages:

    -   tidyverse

    -   rmarkdown

    -   knitr

    -   data.validator

    -   dlookr

    -   skimr

    -   visdat

    -   denguedatahub

    -   DSjobtracker

## Data Profiling

Name of the datasets:

`denguedatahub::srilanka_weekly_data`

`denguedatahub::world_annual`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(denguedatahub)
library(tidyverse)
```

### Data Description: `denguedatahub::srilanka_weekly_data`

```{r, echo=FALSE}
library(skimr)
skim(srilanka_weekly_data)
```

### Data Description: `denguedatahub::world_annual`

```{r, echo=FALSE}
library(skimr)
skim(world_annual)
```

## Variable Types

### `denguedatahub::srilanka_weekly_data`

```{r, echo=FALSE}
library(visdat)
vis_dat(srilanka_weekly_data)
```

Question: Why is there no observable variability in the `cases` column?

### `denguedatahub::world_annual`

This example shows how to work with a large dataset with `visdat`

```{r, echo=FALSE}
world_annual |>
  dplyr::slice(1:1000) |>
  vis_dat()
```

## Visualising Numerial Data

### `denguedatahub::srilanka_weekly_data`

```{r, echo=FALSE}
srilanka_weekly_data |>
  select(where(is.numeric)) |>
  vis_value()
```

### `denguedatahub::world_annual`

```{r, echo=FALSE}
world_annual |>
  slice(1:1000) |>
  select(where(is.numeric)) |>
  vis_value()
```

## Arrange Data Before Plotting Numeric Variables


### `denguedatahub::srilanka_weekly_data`

```{r, echo=FALSE}
srilanka_weekly_data |>
  select(where(is.numeric)) |>
  arrange(cases) |>
  vis_value()
```

## Visualise Binary Variables in the Data

```{r}
## Sample dataset
df1 <- tibble(x=rep(c(1, 0), 50), y=c(rep(1, 50), rep(0, 50)))
```

```{r, echo=FALSE}
vis_binary(df1)
```