# Data Quality Analysis

## Required software and packages

1. R Software

2. RStudio

3. Following packages:

    - tidyverse
  
    - rmarkdown
    
    - knitr
  
    - data.validator
  
    - dlookr
    
    - skimr
    
    - visdat
  
    - denguedatahub
  
    - DSjobtracker


## Data Profiling

Name of the datasets:

`denguedatahub::srilanka_weekly_data`

`denguedatahub::world_annual`

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(denguedatahub)
```

### Data Description: `denguedatahub::srilanka_weekly_data`

```{r, echo=FALSE}
library(skimr)
skim(srilanka_weekly_data)
```

### Data Description: `denguedatahub::world_annual`

```{r, echo=FALSE}
library(skimr)
skim(world_annual)
```


## Variable Types

### `denguedatahub::srilanka_weekly_data`

```{r, echo=FALSE}
library(visdat)
vis_dat(srilanka_weekly_data)
```

### `denguedatahub::world_annual`

This example shows how to work  with a large dataset with `visdat`

```{r, echo=FALSE}
world_annual |>
  dplyr::slice(1000) |>
  vis_dat()
```