---
title: " Predictive modelling: Measures of Accuracy"
---

## Packages

```{r, warnings=FALSE, message=FALSE}
library(tidymodels)
library(tidyverse)
library(gt)
library(stringr)
library(visdat)
library(GGally)
```

## Import Data and Check Data Format

```{r, echo=TRUE, warning=FALSE}
link <- "https://raw.githubusercontent.com/kirenz/datasets/master/housing_unclean.csv"
hdf <- read_csv(link) #readr
dim(hdf)
colnames(hdf)
#View(hdf)
head(hdf) |>
  gt()
```

```{r, echo=TRUE, warning=FALSE}
hdf |> 
  slice_head(n=6) |>
  gt()
```

## Preprocessing

```{r, echo=TRUE, warning=FALSE}
hdf <- 
  hdf |>
  mutate(
    housing_median_age=str_remove_all(housing_median_age, "[years]"),
    median_house_value = str_remove_all(median_house_value, "[$]"))
#View(hdf)
```

### Recheck the format

```{r, echo=TRUE, warning=FALSE}
glimpse(hdf) 
```

### Visualize the structure

```{r, echo=TRUE, warning=FALSE}
vis_dat(hdf)
```

### Observe summary statistics

```{r, echo=TRUE, warning=FALSE}
hdf |>
  count(ocean_proximity, sort=TRUE)
```

### Convert qualitative variables into factor

```{r, echo=TRUE, warning=FALSE}
hdf <- hdf |>
  mutate(across(where(is.character), as.factor))
vis_dat(hdf)
```

### Convert variables into numeric

```{r, echo=TRUE, warning=FALSE}
hdf <- hdf |>
  mutate(
    housing_median_age = as.numeric(housing_median_age),
    median_house_value = as.numeric(median_house_value)
  )
vis_dat(hdf)
```

### Observe missing value

```{r, echo=TRUE, warning=FALSE}
vis_miss(hdf, sort_miss=TRUE)
is.na(hdf) |> colSums()
```

## Create new variables

```{r, echo=TRUE, warning=FALSE}
hdf <- hdf |>
  mutate(rooms_per_household = total_rooms/households,
         bedrooms_per_room = total_bedrooms/total_rooms,
         population_per_household = population/households)

#View(hdf)
```

## Categorize the dependent variable

```{r, echo=TRUE, warning=FALSE}
hdf <- hdf |>
  mutate(price_category = case_when(
    median_house_value < 1500 ~ "below",
    median_house_value >= 1500 ~ "above",
  )) |>
  mutate(price_category = as.factor(price_category)) |>
  select(-median_house_value)
#View(hdf)
```

## Distribution of the dependent variable

```{r, echo=TRUE, warning=FALSE}
hdf |>
  count(price_category, name="count") |>
  mutate(percent = count/sum(count)) |>
  gt()
```

## Check the structure again

```{r, echo=TRUE, warning=FALSE}
skimr::skim(hdf)
```

## EDA

```{r, echo=TRUE, warning=FALSE}
hdf |>
  select(housing_median_age,
         median_income,
         bedrooms_per_room,
         rooms_per_household,
         population_per_household) |>
  ggscatmat(alpha=0.2)

hdf |>
  ggplot(aes(price_category)) + geom_bar()
```

## Your turn

-   Obtain hex binning scatterplot

-   Obtain scatterplot matrix using ggpairs

## Split data into training and test

```{r, echo=TRUE, warning=FALSE}
hdf_no_na <- hdf |> 
  drop_na()

set.seed(123)
data.split <- initial_split(hdf_no_na,
                            prop=3/4,
                            strata = price_category)
train.data <- training(data.split)
test.data <- testing(data.split)
```

## Build a randomforest model

```{r, echo=TRUE, warning=FALSE}
library(randomForest)
rf <- randomForest(price_category ~ .,
                   data=train.data, 
                   importance=TRUE)
test.data$predict <- predict(rf, test.data)

View(test.data)
```

## Accuracy measures

```{r, echo=TRUE, warning=FALSE}
library(caret)
confusionMatrix(data = test.data$predict,
                reference = test.data$price_category)
```

1.  Sensitivity:.....................

2.  Specificity:.....................

3.  Prevalence:......................

4.  Positive Predictive Value:.....................

5.  Negative Predictive Value:.....................

6.  Detection rate:................

7.  Detection prevalence:....................

8.  Balanced accuracy:........................

9.  Precision:...................

10. Recall:.....................

11. F1 score:......................

## Exercise

Prepare a model to predict `medv` - Median value of owner-occupied homes in \$1000s

R code to load data:

```{r, echo=TRUE, warning=FALSE}
library(mlbench)
data(BostonHousing)
head(BostonHousing)
```

## Data Profiling

```{r, echo=TRUE, warning=FALSE}
skimr::skim(BostonHousing)
```
